Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
check installed packages before knitting and install missing

```{r, setup, echo = FALSE, message=FALSE}
library("officer")
library("dplyr")
library("janitor")
library("here")
library("flextable")
library("Reproducibility.in.Plant.Pathology")
library("tidyr")
library("DiagrammeR")
library("DiagrammeRsvg")
library("rsvg")
library("ggplot2")
library("bayesplot")
library("patchwork")

>>>>

```{r, setup, echo = FALSE, message=FALSE}
library("Reproducibility.in.Plant.Pathology")

packages <- c(
  "officer",
  "dplyr",
  "janitor",
  "here",
  "flextable",
  "tidyr",
  "DiagrammeR",
  "DiagrammeRsvg",
  "rsvg",
  "ggplot2",
  "bayesplot",
  "patchwork"
)

install.packages(setdiff(packages, rownames(installed.packages())))
